Investigate relations in incomplete datasets to inform imputation model

### 2020-02-17 3.Thesis/inspect_incomplete_data.Rmd
used map to create density plots and tests for all missingness indicators at once.

```{r echo=TRUE, message=FALSE, warning=FALSE}
# set-up environment
library(mice) # Data imputation
library(dplyr) # Data manipulation
library(magrittr)
library(broom)
library(ggplot2)
set.seed(123)
```

@@

```{r}
# pre-processing
Rgen <- is.na(boys$gen)
levels(Rgen) <- c("Missing", "Observed")
data <- boys %>% as_tibble %>% cbind(Rgen)

# plot relation between observed values in age and missingness in gen
data %>%
  ggplot(aes(x = age, fill = is.na(gen))) +
  geom_histogram(aes(y = 100 * ..density..),
                 alpha = 0.5,
                 position = 'identity') +
  xlab("Age (years)") +
  ylab("Percentage observed") +
  scale_fill_manual(
    name = "Gen",
    breaks = c("FALSE", "TRUE"),
    labels = c("Observed", "Missing"),
    values = c("#006CC2", "#B61A51")
  )

# evaluate statistically
out_Rgen <- data %>% lm(age ~ is.na(gen), data = .)
out_int <- data %>% lm(age ~ 1, data = .)
anova(out_int, out_Rgen)
```

@@

```{r}
out_gen <- data %>% lm(age ~ gen, data = .)
out_int_gen <- data %>% filter(!is.na(gen)) %>% lm(age ~ 1, data = .)
anova(out_int_gen, out_gen)
```

@@

>>>>

# Part 1: Use 1 variable from 1 dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
# set-up environment
library(mice) # Data imputation
library(dplyr) # Data manipulation
library(magrittr)
library(broom)
library(ggplot2)
library(purrr)
set.seed(123)
```

@@

```{r}
# # pre-processing
# Rgen <- is.na(boys$gen)
# levels(Rgen) <- c("Missing", "Observed")
dat <- boys # %>% as_tibble # %>% cbind(Rgen)

# plot relation between observed values in age and missingness in gen
dat %>%
  ggplot(aes(x = age, fill = is.na(gen))) +
  geom_histogram(aes(y = 100 * ..density..),
                 alpha = 0.5,
                 position = 'identity') +
  xlab("Age (years)") +
  ylab("Percentage observed") +
  scale_fill_manual(
    name = "Gen",
    breaks = c("FALSE", "TRUE"),
    labels = c("Observed", "Missing"),
    values = c("#006CC2", "#B61A51")
  )

# evaluate statistically
out_Rgen <- dat %>% lm(age ~ is.na(gen), data = .)
out_int <- dat %>% lm(age ~ 1, data = .)
anova(out_int, out_Rgen)
```

**To do:** Create a similar plot for categorical outcome variable.

@@

```{r}
out_gen <- dat %>% lm(age ~ gen, data = .)
out_int_gen <- dat %>% filter(!is.na(gen)) %>% lm(age ~ 1, data = .)
anova(out_int_gen, out_gen)
```

@@

# Part 2: Use any variable from 1 dataset

To apply these evaluations to all variables, we need a function. 
```{r}
# explore map functionalities
test_miss <- function(.x){
  return(is.na(.x))
}
map(c(1, NA, 4, 7), test_miss)

# inline function
map_df(c(1, NA, 4, 7), function(.x) {
  return(data.frame(entry = .x, 
                    is_NA = test_miss(.x)))
})

# shorter inline function
map_df(c(1, NA, 4, 7), ~{
  return(data.frame(entry = .x, 
                    is_NA = test_miss(.x)))
})

# test map functionalities
dat %>%  map_df(is.na)
dat %>% map_df(~(data.frame(n_miss = sum(is.na(.x)),
                                  class = class(.x))),
                     .id = "variable")

# apply map to our own problem
interc_only <- dat %>% lm(age ~ 1, data = .)
#age <- dat[,1]
# output_for_table <- dat %>% 
#   map(~{lm(dat$age~is.na(.x)) %>% 
#       anova(interc_only, .)}, .id = "variable")
dat %>% 
  map(~{lm(age~is.na(.x), data = dat) %>% anova(interc_only, .)})

# this works, but only for age as outcome. now apply to all variables.

```

**Question:** how do we evaluate these? Just look at p-values? Then, do we need some alpha inflation correction?

Also create the density plots for all missingness indicators.

```{r}
# plot this for each missingness indicator
dat %>%
  map(~{ggplot(data=dat, aes(x = age, fill = is.na(.x))) +
  geom_histogram(aes(y = 100 * ..density..),
                 alpha = 0.5,
                 position = 'identity') +
  xlab("Age (years)") +
  ylab("Percentage observed") +
  scale_fill_manual(
    name = names(.),
    breaks = c("FALSE", "TRUE"),
    labels = c("Observed", "Missing"),
    values = c("#006CC2", "#B61A51")
  )})

# only the name of the legend does not work. maybe look into pmap?
```

# Part 3: Use any variable from any dataset
